---
title       : Course Project Shiny Application and Reproducible Pitch
subtitle    : 
author      : ezwanderis
job         : 
framework   : io2012
highlighter : highlight.js
hitheme     : tomorrow
widgets     : []
mode        : selfcontained 
knit        : slidify::knit2slides
---

## Overview

This slides is a part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The Shiny app is avalilable at: 
https://ezwanderis.shinyapps.io/CarSelection/

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/ezwanderis/data-product/

---
## Web Application functionality

The sites is providing a tools for to select the best car for your trip.

We required you provide your trip detail like distance of your trip and the price od gasoline in your region, it's needed to calculate the Gasoline Expenditure for each car. Next with provide your budget on gasoline, so we can filtered and show the car with has Miles per Gallon(MPG) that below your budget.

Second, you can choose your desire cars characteristic in term of : Cylinders, Displacement, Horse Power and Transmission.

The result contains filters selected cars will show in a table on the main content with using the mtcars dataset from [R].

---
## MTCARS Dataset
The data used in the app comes from the Motor Trend Car Road Tests (mtcars) dataset. Let has a look on the mtcars's summary
```{r, echo=FALSE}
summary(mtcars)
```

---
## Plot
The relationship between miles per gallon (mpg) and displacement (disp) in the mtcars dataset.
```{r, echo=FALSE}
plot(mpg ~ disp, mtcars)

```



